---
title: "Project_R_MarkdownandLeaflet"
author: "Marco Antonio Lopez"
date: "2023-02-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Project 1 Marco Lopez

Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

First Step: Install leaflet
install.packages("leaflet")

```{r}
library(leaflet)
```

## My Institution and my School

```{r chunk 1}
place <- c("Instituto de Geografia", "Facultad de Ingenieria")
place_links <- c("<a href='https://www.geografia.unam.mx/geoigg/'>Geografia</a>", "<a href='https://www.ingenieria.unam.mx/'>Ingenieria</a>")
lat <- c(19.32801, 19.33113)
lng <- c(-99.17641, -99.18468)
df <- data.frame(place, place_links, lat, lng)
library(leaflet)
df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(lat=lat, lng=lng, popup=place_links, clusterOptions=markerClusterOptions)

